### 2022-12-17 Rmd/Analyse changes in mackerel.Rmd
Restructured into Rmd folder

  geom_segment(aes(x=2008, xend=2012, y=2000000, yend=2000000), colour="red", size=2) +
  geom_segment(aes(x=2013, xend=2019, y=2000000, yend=2000000), colour="pink", size=2) +
  geom_dl(aes(x=2008, y=1800000, label="ica"), colour="red", method = list(dl.combine("last.points") ) )  +
  geom_dl(aes(x=2013, y=1800000, label="sam"), colour="pink", method = list(dl.combine("last.points") )) +

>>>>

  geom_line(aes(size=purpose)) +
  geom_line(data=ass_final, aes(colour=purpose ), size=1.5) +
  # geom_dl(aes(label  = ayear, group=purpose), method = list(dl.combine("last.points"), cex = 0.8)) +

  # geom_segment(aes(x=2008, xend=2012, y=2000000, yend=2000000), colour="red", size=2) +
  # geom_segment(aes(x=2013, xend=2019, y=2000000, yend=2000000), colour="pink", size=2) +
  # geom_dl(aes(x=2008, y=1800000, label="ica"), colour="red", method = list(dl.combine("last.points") ) )  +
  # geom_dl(aes(x=2013, y=1800000, label="sam"), colour="pink", method = list(dl.combine("last.points") )) +

### 2022-12-17 Rmd/Analyse changes in pelagic stocks.Rmd
Restructured into Rmd folder

# -----------------------------------------------------------------------------------------------
# Analyse zero catch advice.Rmd
#
# 26/02/2020 adapted from Analyse changes in pelagic stocks
# -----------------------------------------------------------------------------------------------

@@

  # filter(grepl("mac-67|mac-nea|whb-c|whb-n|her-noss|her-47d3",
  #              stockkeylabelold)) %>%
  # filter(grepl("her-47|mac-67|mac-nea|whb-c|whb-n|hom-c|hom-w|her-3a22|her-noss",
  #              stockkeylabelold)) %>%
  # filter(grepl("mac-67|mac-nea", 
  #              stockkeylabelold)) %>%

@@

  filter(assessmentyear >= 2000) %>% 
  ungroup()

@@

**Analysis of zero catch advice**

@@

adv %>% 
  filter(purpose == "advice") %>% 
  filter(advisedlandingsmax == 0 | advisedcatchmax == 0) %>%  
  filter(tacyear <= 2018) %>% 
  filter(!is.na(tal)) %>% 
  dplyr::select(speciesfaocode, stockkeylabelold, assessmentyear, tacyear, advisedlandingsmax, tal, landings, catches) %>%
  ungroup() %>% 
  mutate(catch     = ifelse(!is.na(catches), catches, landings)) %>% 
  mutate(zerotac   = ifelse(tal   == 0, 1, 0)) %>% 
  mutate(zerocatch = ifelse(catch == 0, 1, 0)) %>% 
  # View()
  group_by(tacyear) %>% 
  summarize(nzeroadvice = n(),
            nzerotac    = sum(zerotac, na.rm=TRUE),
            nzerocatch  = sum(zerocatch, na.rm=TRUE)) %>% 
  gather(key="variable", value="data", nzeroadvice:nzerocatch) %>%

  geom_line(aes(y=data, group=variable, colour=factor(variable))) +
  geom_point(aes(y=data, group=variable, colour=factor(variable))) +

  scale_x_continuous(breaks=pretty_breaks()) +
  expand_limits(y=0) + 
  labs(y="N stocks") 
#  facet_wrap(~variable)

adv %>% 
  filter(purpose == "advice") %>% 
  filter(advisedlandingsmax == 0 | advisedcatchmax == 0) %>%  
  filter(tacyear <= 2018) %>% 
  filter(!is.na(tal)) %>% 
  dplyr::select(speciesfaocode, stockkeylabelold, stockkeylabelnew, assessmentyear, tacyear, advisedlandingsmax, tal, landings, catches) %>%
  ungroup() %>% 
  mutate(catch     = ifelse(!is.na(catches), catches, landings)) %>% 
  mutate(zerotac   = ifelse(tal   == 0, 1, 0)) %>% 
  mutate(zerocatch = ifelse(catch == 0, 1, 0)) %>%

  write.csv(file="zerocatch.csv", row.names = FALSE)

>>>>

# -----------------------------------------------------------------------------------------------
# Analyse changes in pelagic stocks.Rmd
#
# 07/01/2019 first coding; adapted from ICES advice and assessment summaries.Rmd
# 10/01/2018 made small changes to the table
# 04/05/2019 updated for WKRRMAC 2019; focus on mackerel
# 06/06/2019 changed the data frame d; now also has purpose
# 03/09/2019 updated after WGWIDE 2019
# 02/10/2019 updated for pelagic forum
# -----------------------------------------------------------------------------------------------

@@

  filter(grepl("mac-67|mac-nea|whb-c|whb-n|her-noss|her-47d3",
               stockkeylabelold)) %>%
  # filter(grepl("her-47|mac-67|mac-nea|whb-c|whb-n|hom-c|hom-w|her-3a22|her-noss",
  #              stockkeylabelold)) %>%
  # filter(grepl("mac-67|mac-nea", 
  #              stockkeylabelold)) %>%

@@

  filter(assessmentyear >= 2008) %>% 
  ungroup()

@@

**Analysis of advice changes in a number of key pelagic stocks**

@@

### 2022-12-17 Rmd/ICES advice and assessment summaries HAWG 2020.Rmd
Restructured into Rmd folder

# -----------------------------------------------------------------------------------------------
# ICES advice and assessment summaries.Rmd
#
# 06/07/2018 first coding
# 14/12/2018 updated for the new database structure
# 01/06/2019 updated for herring advice round
# 03/09/2019 updated after WGWIDE
# -----------------------------------------------------------------------------------------------

@@

# Libraries
library(rmarkdown) # creating markdown documents
library(tidyverse) # combined package of dplyr, tidyr, ggplot, readr, purrr and tibble
library(reshape2)  # reshaping data; e.g. dcast
library(ggthemes)  # for themes
library(pander)    # for print tables
library(readxl)    # read excel files
library(cowplot)   # multiplots
library(directlabels)  # label graphs
library(RColorBrewer) # colours
library(lubridate)

# Load utils code
source("../../mptools/r/my_utils.r")

@@

# Load dataset
load(file=paste(dropboxdir, "/rdata/iAssess.RData",sep=""))
load(file=paste(dropboxdir, "/rdata/iAdvice.RData",sep=""))

fay <- 2011
fy  <- 2000
lay <- 2019
ly  <- 2019

stock="hom-nsea"
assessyear=lay
assessyear=2017

firstyear=fy
lastyear=ly
plot = c("stocksize", "fishingpressure", "recruitment")
my.purpose="advice"

# Function to plot single assessment
plot_assess <- function(stock,assessyear, firstyear, lastyear, 
                        my.purpose = "advice", plot=c("stocksize","fishingpressure")) {

  d <-
    iAssess %>% 
    ungroup() %>%

    filter(stockkeylabelold %in% stock | stockkeylabel %in% stock) %>% 
    filter(assessmentyear   == assessyear) %>% 
    filter(year             %in% firstyear:lastyear) %>% 
    filter(purpose %in% my.purpose) %>%

    #set type
    mutate(
      type = ifelse(purpose == "advice"      , "last"    , NA),
      type = ifelse(grepl("bench",purpose)   ,  "benchmark", type),
      type = ifelse(grepl("replaced",purpose), "replaced"  , type),
      type = ifelse(is.na(type), "other", type)) %>%

    mutate(tyear     = substr(as.character(assessmentyear), 3,4)) %>% 
    dplyr::select(stockkeylabel, stockkeylabelold, stockdescription, type, 
                  assessmentyear, year,
                  recruitment, lowrecruitment, highrecruitment, unitofrecruitment,
                  stocksize, lowstocksize, highstocksize, stocksizeunits,
                  fishingpressure, lowfishingpressure, highfishingpressure, fishingpressureunits,
                  landings, discards, catches, catcheslandingsunits) %>%

    # convert to long data
    gather(key=variable, value=data, c(recruitment, lowrecruitment, highrecruitment, 
                  stocksize, lowstocksize, highstocksize,
                  fishingpressure, lowfishingpressure, highfishingpressure, 
                  landings, discards, catches)) %>%

    # set appropriate units and remove old units columns
    mutate(
      unit = ifelse(grepl("recruitment", variable), unitofrecruitment, NA),
      unit = ifelse(grepl("stocksize"  , variable), stocksizeunits, unit),
      unit = ifelse(grepl("fishing"    , variable), fishingpressureunits, unit),
      unit = ifelse(grepl("landing|discard|catch", variable), catcheslandingsunits, unit) ) %>% 
    dplyr::select(-unitofrecruitment, - stocksizeunits, -fishingpressureunits, -catcheslandingsunits) %>%

    # separate estimate, low and high
    mutate(
      esttype = ifelse(grepl("low", variable), "low", NA),
      esttype = ifelse(grepl("high", variable), "high", esttype),
      esttype = ifelse(is.na(esttype), "est", esttype) ) %>% 
    mutate(
      variable = gsub("low|high","", variable) ) %>%

    # select variables to plot
    filter(variable %in% plot) %>% 
    mutate(variable = factor(variable, levels=plot, ordered=TRUE)) %>%

    # spread to make separate columns for est, low and high
    spread(key=esttype, value=data)

  # Reference points
  rp <-
    iAdvice %>% 
    ungroup() %>% 
    filter(purpose %in% my.purpose) %>% 
    filter(stockkeylabelold %in% stock | stockkeylabel %in% stock) %>% 
    filter(assessmentyear   == assessyear) %>% 
    dplyr::select(stockkeylabel, stockkeylabelold, assessmentyear,
              blim, bpa, msybtrigger, flim, fpa, fmsy) %>%
    gather(key=refpoint, value=data, blim:fmsy) %>%

    # generate variables
    mutate(
      variable = ifelse(refpoint %in% c("blim","bpa","msybtrigger"), "stocksize", NA),
      variable = ifelse(refpoint %in% c("flim", "fpa", "fmsy"), "fishingpressure", variable) ) %>% 
    mutate(variable = factor(variable, levels=plot, ordered=TRUE)) %>%

    # generate refpoint types
    mutate(
      reftype = ifelse(refpoint %in% c("blim","flim"), "lim", NA),
      reftype = ifelse(refpoint %in% c("bpa", "fpa") , "pa", reftype),
      reftype = ifelse(refpoint %in% c("msybtrigger", "fmsy"), "msy", reftype))  %>% 
    dplyr::select(-refpoint)

  # Titles
  tt <-
    d %>% 
    distinct(variable, unit, stockkeylabel, stockdescription) %>%
    filter(!is.na(unit))

  # d %>% View()

  # plot 
  d %>%

    ggplot(aes(x=year,y=est)) +

    theme_publication() +

    theme(legend.title=element_blank(),
          axis.text.x = element_text(angle = 0, vjust = 0.5, size=9),
          axis.text.y = element_text(size=9),
          plot.title  = element_text(size=10, hjust=0), 
          plot.margin = margin(2, 2, 2, 2, "mm"),
          # strip.background = element_blank(),
          legend.position = "null") +

    geom_ribbon(aes(x=year, ymin=low, ymax=high, fill=type), alpha=0.2) +

    geom_line(aes(colour = type, size=type, linetype=type) ) +

    # geom_ribbon(aes(ymin=low, ymax=high), alpha=0.2, fill="red") +
    # geom_line(colour="red" ) +

    # plot limits
    geom_hline(data=filter(rp, reftype %in% "lim"), aes(yintercept=data), 
               colour="red", linetype="solid", inherit.aes=FALSE) +
    geom_text (data=filter(rp, reftype %in% "lim"), aes(x=firstyear, y=data), 
               label = "lim", vjust = -0.3, hjust = 0, colour="red", inherit.aes=FALSE) +

    # plot msy
    geom_hline(data=filter(rp, reftype %in% "msy"), aes(yintercept=data), 
               colour="red", linetype="dashed", inherit.aes=FALSE) +
    geom_text (data=filter(rp, reftype %in% "msy"), aes(x=firstyear, y=data), 
               label = "msy", vjust = -0.3, hjust = 0, colour="red", inherit.aes=FALSE) +

    scale_colour_manual  (
      values=c(last ="red",last_bench="blue",advice="black",
               benchmark="blue",replaced="green",other="gray80")) +
    scale_fill_manual    (
      values=c(last = "red",last_bench="blue",advice="black",
               benchmark="blue",replaced="green",other="gray80")) +
    scale_linetype_manual(
      values=c(last="solid",last_bench="solid",advice="solid",
               benchmark="solid",replaced="solid",other="solid")) +
    scale_size_manual    (
      values=c(last= 1.2,last_bench=1.2,advice=0.8,
               benchmark=0.8,replaced=0.8,other=0.8)) +

    expand_limits(y = 0) +
    xlim(firstyear,lastyear) +
    labs(x = NULL, y = NULL, 
         title = paste0(unique(tt$stockdescription), " (", unique(tt$stockkeylabel),")") ) +
    facet_wrap(~variable, scales="free_y")

  } # End of plot_assess function

# s   <- "mac-nea"
# plot_assess(stock=s,assessyear=lay, firstyear=fy, lastyear=ly, 
#             plot = c("stocksize", "fishingpressure", "recruitment"), 
#             my.purpose="advice")
# plot_assess(stock=s,assessyear=lay, firstyear=fy, lastyear=ly, 
#             plot = c("stocksize", "fishingpressure", "recruitment"), 
#             my.purpose="bench")

stock="whb-comb"
firstassessyear=fay; lastassessyear=lay; firstyear=fy;lastyear=ly;
plot = c("stocksize", "fishingpressure")
include.benchmark=TRUE; include.replaced=TRUE
plot.uncertainty=FALSE

# Function to plot historical assessments
plot_history <- function(stock,firstassessyear,lastassessyear, firstyear, lastyear, 
                         include.benchmark = TRUE, include.replaced=TRUE, 
                         plot=c("stocksize","fishingpressure"),
                         plot.uncertainty=FALSE) {

  d <-
    iAssess %>% 
    ungroup() %>%

    {if (include.benchmark == TRUE & include.replaced == TRUE) {
      filter(., purpose %in% c("advice","benchmark", "interbenchmark", "bench", "replaced"))
    } else if (include.benchmark == TRUE & include.replaced == FALSE) {
      filter(., purpose %in% c("advice","benchmark", "interbenchmark", "bench"))
    } else if (include.benchmark == FALSE & include.replaced == TRUE) {
      filter(., purpose %in% c("advice","replaced"))
    } else {
      filter(., purpose %in% c("advice")) 
    }} %>%

    filter(stockkeylabelold %in% stock | stockkeylabel %in% stock) %>% 
    filter(assessmentyear   %in% c(firstassessyear:lastassessyear)) %>% 
    filter(year             %in% firstyear:lastyear) %>%

    group_by(assessmentyear) %>%

    #set type
    mutate(
      type = ifelse(assessmentyear == lastassessyear & purpose == "advice"      , "last"      , NA),
      type = ifelse(assessmentyear == lastassessyear & grepl("bench",purpose) & 
                    n_distinct(purpose)==1, "last_bench", type),
      type = ifelse(assessmentyear == lastassessyear & grepl("bench",purpose) & 
                      n_distinct(purpose) > 1, "bench", type),
      type = ifelse(assessmentyear != lastassessyear & purpose == "advice"      , "advice"    , type),
      type = ifelse(assessmentyear != lastassessyear & grepl("bench",purpose)   ,  "benchmark", type),
      type = ifelse(assessmentyear != lastassessyear & grepl("replaced",purpose), "replaced"  , type),
      type = ifelse(is.na(type), "other", type)) %>%

    ungroup() %>%

    # set tyear and group
    mutate(tyear = substr(as.character(assessmentyear), 3,4)) %>% 
    mutate(group = paste0(tyear, type)) %>% 
    mutate(group = substr(group, 1,3)) %>% 
    mutate(group = gsub("a|l","", group)) %>%

    dplyr::select(stockkeylabel, stockkeylabelold, stockdescription, 
                  assessmentyear, year, tyear, group, type, purpose,
                  recruitment, lowrecruitment, highrecruitment, unitofrecruitment,
                  stocksize, lowstocksize, highstocksize, stocksizeunits,
                  fishingpressure, lowfishingpressure, highfishingpressure, fishingpressureunits,
                  landings, discards, catches, catcheslandingsunits) %>%

    # convert to long data
    gather(key=variable, value=data, 
           c(recruitment, lowrecruitment, highrecruitment, 
             stocksize, lowstocksize, highstocksize,
             fishingpressure, lowfishingpressure, highfishingpressure, 
             landings, discards, catches)) %>%

    # set appropriate units and remove old units columns
    mutate(
      unit = ifelse(grepl("recruitment", variable), unitofrecruitment, NA),
      unit = ifelse(grepl("stocksize"  , variable), stocksizeunits, unit),
      unit = ifelse(grepl("fishing"    , variable), fishingpressureunits, unit),
      unit = ifelse(grepl("landing|discard|catch", variable), catcheslandingsunits, unit) ) %>% 
    dplyr::select(-unitofrecruitment, - stocksizeunits, -fishingpressureunits, -catcheslandingsunits) %>%

    # separate estimate, low and high
    mutate(
      esttype = ifelse(grepl("low", variable), "low", NA),
      esttype = ifelse(grepl("high", variable), "high", esttype),
      esttype = ifelse(is.na(esttype), "est", esttype) ) %>% 
    mutate(
      variable = gsub("low|high","", variable) ) %>%

    # select variables to plot
    filter(variable %in% plot) %>% 
    mutate(variable = factor(variable, levels=plot, ordered=TRUE)) %>%

    # spread to make separate columns for est, low and high
    spread(key=esttype, value=data) %>%

    # remove NA
    filter(!is.na(est))

  # Check
  # d %>% filter(assessmentyear == 2019) %>% View()

  # Reference points
  rp <-
    iAdvice %>% 
    ungroup() %>% 
    filter(purpose %in% my.purpose) %>% 
    filter(stockkeylabelold %in% stock | stockkeylabel %in% stock) %>% 
    filter(assessmentyear   == assessyear) %>% 
    dplyr::select(stockkeylabel, stockkeylabelold, assessmentyear,
              blim, bpa, msybtrigger, flim, fpa, fmsy) %>%
    gather(key=refpoint, value=data, blim:fmsy) %>%

    # generate variables
    mutate(
      variable = ifelse(refpoint %in% c("blim","bpa","msybtrigger"), "stocksize", NA),
      variable = ifelse(refpoint %in% c("flim", "fpa", "fmsy"), "fishingpressure", variable) ) %>% 
    mutate(variable = factor(variable, levels=plot, ordered=TRUE)) %>%

    # generate refpoint types
    mutate(
      reftype = ifelse(refpoint %in% c("blim","flim"), "lim", NA),
      reftype = ifelse(refpoint %in% c("bpa", "fpa") , "pa", reftype),
      reftype = ifelse(refpoint %in% c("msybtrigger", "fmsy"), "msy", reftype))  %>% 
    dplyr::select(-refpoint)

  # Titles
  tt <-
    d %>% 
    distinct(variable, unit, stockkeylabel, stockdescription) %>%
    filter(!is.na(unit))

  # plot
  d %>%

    ggplot(aes(year,est, group=group)) +

    theme_publication() +

    theme(legend.title=element_blank(),
          axis.text.x = element_text(angle = 0, vjust = 0.5, size=9),
          axis.text.y = element_text(size=9),
          plot.title  = element_text(size=10, hjust=0), 
          plot.margin = margin(2, 2, 2, 2, "mm"),
          # strip.background = element_blank(),
          legend.position = "null") +

    {if (plot.uncertainty)     
      geom_ribbon(data=filter(d, type=="last"),
          aes(x=year, ymin=low, ymax=high, fill=type), alpha=0.2) } +

    geom_line(aes(colour = type, size=type, linetype=type) ) +

    geom_dl(aes(label  = group, colour = type, group=group), 
            method = list(dl.combine("last.points"), cex = 0.8, inherit.aes=FALSE)) +

    # plot limits
    geom_hline(data=filter(rp, reftype %in% "lim"), aes(yintercept=data), 
               colour="red", linetype="solid", inherit.aes=FALSE) +
    geom_text (data=filter(rp, reftype %in% "lim"), aes(x=firstyear, y=data), 
               label = "lim", vjust = -0.3, hjust = 0, colour="red", inherit.aes=FALSE) +

    # plot msy
    geom_hline(data=filter(rp, reftype %in% "msy"), aes(yintercept=data), 
               colour="red", linetype="dashed", inherit.aes=FALSE) +
    geom_text (data=filter(rp, reftype %in% "msy"), aes(x=firstyear, y=data), 
               label = "msy", vjust = -0.3, hjust = 0, colour="red", inherit.aes=FALSE) +

    scale_colour_manual  (
      values=c(last ="red",last_bench="blue",advice="black",
               benchmark="blue",replaced="green",other="gray80")) +
    scale_fill_manual    (
      values=c(last = "red",last_bench="blue",advice="black",
               benchmark="blue",replaced="green",other="gray80")) +
    scale_linetype_manual(
      values=c(last="solid",last_bench="solid",advice="solid",
               benchmark="solid",replaced="solid",other="solid")) +
    scale_size_manual    (
      values=c(last= 1.2,last_bench=1.2,advice=0.8,
               benchmark=0.8,replaced=0.8,other=0.8)) +

    expand_limits(y = 0) +
    xlim(firstyear,lastyear) +
    labs(x = NULL, y = NULL, 
         title = paste0(unique(tt$stockdescription), " (", unique(tt$stockkeylabel),")") ) +
    facet_wrap(~variable, scales="free_y")

  # return(d)

  } # End of plot_history function

# firstadviceyear <- 2016; lastadviceyear  <- 2020; stock<-c("mac-nea"); include.replaced <- TRUE

# Function to plot advice overviews
table_advice <- function(stock,firstadviceyear,lastadviceyear, include.replaced=FALSE) {

  d <-
    iAdvice %>%

    filter(stockkeylabelold %in% stock | stockkeylabel %in% stock) %>%

    filter(tacyear %in% firstadviceyear:lastadviceyear) %>%

    {if (include.replaced == TRUE) {
      filter(., purpose %in% c("advice","replaced"))
    } else {
      filter(., purpose %in% c("advice")) 
    }} %>%

    mutate(advicebasis= substr(advicebasis,1,25),

           advice     = ifelse(!is.na(advisedcatchmax), advisedcatchmax, advisedlandingsmax),
           advicemax  = ifelse(!is.na(advisedcatchmax), advisedcatchmax, advisedlandingsmax),
           advicetype = ifelse(!is.na(advisedcatchmax), "catch", "landings"),

           tac        = ifelse(!is.na(tac), tac, tal),
           tactype    = ifelse(!is.na(tac), "catch", "landings"),

           catch      = ifelse(!is.na(catches), catches, NA),
           catchtype  = ifelse(!is.na(catches), "catches", ""),

           catchtype  = ifelse(!is.na(landings) & is.na(catch), "landings", catchtype),
           catch      = ifelse(!is.na(landings) & is.na(catch), landings, catch),

           catchtype  = ifelse(!is.na(officiallandings) & is.na(catch), "officiallandings", catchtype),
           catch      = ifelse(!is.na(officiallandings) & is.na(catch), officiallandings, catch),

           adv_c      = 100 * (advicemax / lag(advicemax, n=1) - 1),
           tac_c      = 100 * (tac /lag(tac, n=1) - 1),
           cat_c       = 100 * (catch / lag(catch, n=1) -1)
           ) %>%

    select(stockkeylabel, tacyear, advicebasis, purpose, advice, fadvmax, advicemax, tac, catch, 
           adv_c, tac_c, cat_c,
           advicetype, tactype, catchtype)

  d %>% 
  select("stockkeylabel", "tacyear", "advicebasis", "purpose", "fadvmax", "advicemax", "tac", "catch") %>%
  arrange(tacyear, desc(purpose)) %>% 
  pandoc.table(., 
               style        = "simple",
               split.tables = 200, 
               justify      = "right",
               missing      =" ",
               big.mark     = '', 
               round        = c(0,0,0,2,2,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))
}

# table_advice(stock=s,firstadviceyear=fay+1,lastadviceyear=lay+1, include.replaced = TRUE)

@@

**Summary of ICES 2019 WGWIDE assessments and advice**

@@

plot_history(stock=s,firstassessyear=fay,lastassessyear=lay, firstyear=fy, lastyear=ly, 
             include.benchmark = TRUE, 
             plot = c("stocksize", "fishingpressure")) 
```

@@

@@

_Table 1 Northeast Atlantic mackerel. History of advice, tac and catch._

@@

@@

@@

@@

@@

@@

@@

*North Sea horse mackerel*

The assessment and advice of North Sea is carried out every second year. A new stock assessor was responsible for the assessment (as the previous stock assessor changed jobs), and she found a number of errors in the codes that had been used in 2017. These errors were now corrected and lead to a much lower estimate of stock size in 2016.

This is a so-called category 3 advice, which means that it only uses the relative trend in a (combined) survey to derive the advice. The trend is based on the abundance of the North Sea IBTS survey (quarter 3) and French Channel CGFS survey (quarter 4). The stock is considered to be at a low level even though recruitment appears to have been higher in recent year. A length-based proxy indicator suggests that fishing mortality is probably (just) above Fmsy.

The advice is lower than the advice presented in 2017. Note that the advice is a catch advice. The advice for the landed part is 13305 t.The advice is applicable for 2020 and 2021.

s   <- "hom-nsea"

_Figure 4a North Sea horse mackerel. Summary of most recent assessment_

s   <- "hom-nsea"

_Figure 4b North Sea horse mackerel. History of assessments. Red is most recent assessment, black is earlier assessments and blue is benchmarks. _

s   <- "hom-nsea"

_Table 4 North Sea horse mackerel. History of advice, tac and catch._

@@

_Figure 5a Atlanto-scandian herring. Summary of most recent assessment_

@@

@@

_Figure 5b Atlanto-scandian herring. History of assessments. Red is most recent assessment, black is earlier assessments and blue is benchmarks. _

@@

_Table 5 Atlanto-scandian herring. History of advice, tac and catch._

>>>>

# -----------------------------------------------------------------------------------------------
# ICES advice and assessment summaries.Rmd
#
# 06/07/2018 first coding
# 14/12/2018 updated for the new database structure
# 01/06/2019 updated for herring advice round
# 03/09/2019 updated after WGWIDE
# 30/03/2020 updated after HAWG; UNFINISHED. JUST TEMPORARY SOLUTIONS. 
# -----------------------------------------------------------------------------------------------

@@

# Libraries
library(rmarkdown) # creating markdown documents
library(tidyverse) # combined package of dplyr, tidyr, ggplot, readr, purrr and tibble
library(reshape2)  # reshaping data; e.g. dcast
library(ggthemes)  # for themes
library(pander)    # for print tables
library(readxl)    # read excel files
library(cowplot)   # multiplots
library(directlabels)  # label graphs
library(RColorBrewer) # colours
library(lubridate)
library(ggrepel)

# Load utils code
source("../../mptools/r/my utils.r")
source("iAssess functions.r")

@@

# Load dataset
iAssess <- get(load(file=paste(dropboxdir, "/rdata/iAssess.RData",sep=""))) %>%

  # fix for 67bc in 2020
  mutate(purpose = ifelse(stockkeylabelold=="her-67bc" & assessmentyear==2020, "advice", purpose)) %>%

  # fix for North Sea sprat (ignore the realignment)
  mutate(stockkeylabelold = ifelse(stockkeylabel == "spr.27.3a4","spr-nsea", stockkeylabelold))

iAdvice <- get(load(file=paste(dropboxdir, "/rdata/iAdvice.RData",sep="")))

fay <- 2011
fy  <- 2000
lay <- 2020
ly  <- 2020

# iAssess %>% filter(stockkeylabelold=="her-67bc") %>% ungroup() %>% distinct(assessmentyear, purpose)
# iAssess %>% filter(stockkeylabelold=="spr-nsea") %>% ungroup() %>% distinct(assessmentyear, purpose)
# iAssess %>% filter(substr(stockkeylabelold,1,3)=="spr") %>% ungroup() %>% distinct(stockkeylabelold, stockkeylabel, assessmentyear, purpose) %>% View()

@@

**Summary of ICES 2020 WGWIDE assessments and advice**

@@

# s   <- "mac-nea"

plot_history(stock=s,
             firstassessyear=fay,
             lastassessyear=lay, 
             firstyear=fy, 
             lastyear=ly, 
             include.benchmark = TRUE,
             include.replaced = TRUE,
             plot = c("stocksize", "fishingpressure"))

@@

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

plot_advice(stock=s,firstadviceyear=2001,lastadviceyear=lay+1, include.replaced = FALSE)

_Figure 1c Northeast Atlantic mackerel. Top: comparison of (max) scientific advice, TAC (or sum of unilateral quota) and Total Catch. Bottom: percentage deviation from ICES advice, CoA is Catch over Advice, ToA is TAC over Advice. _

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

table_advice(stock=s,firstadviceyear=2001,lastadviceyear=lay+1, include.replaced = FALSE)

@@

_Table 1.a Northeast Atlantic mackerel. History of advice, tac and catch._

@@

# s   <- "whb-comb"

plot_history(stock=s,
             firstassessyear=fay,
             lastassessyear=lay, 
             firstyear=fy, 
             lastyear=ly, 
             include.benchmark = TRUE, 
             include.replaced = FALSE, 
             plot = c("stocksize", "fishingpressure"), 
             plot.uncertainty=TRUE)

@@

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

plot_advice(stock=s,firstadviceyear=2001,lastadviceyear=lay+1, include.replaced = FALSE)

_Figure 1c Blue whiting. Top: comparison of (max) scientific advice, TAC (or sum of unilateral quota) and Total Catch. Bottom: percentage deviation from ICES advice, CoA is Catch over Advice, ToA is TAC over Advice. _

@@

table_advice(stock=s,firstadviceyear=2001,lastadviceyear=lay+1, include.replaced = FALSE)

@@

plot_assess(stock=s,
            assessyear=lay,
            firstyear=fy,
            lastyear=ly,
            plot = c("stocksize", "fishingpressure", "recruitment"),
            my.purpose="advice")

@@

# s   <- "hom-west"

@@

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# s   <- "hom-west"

plot_advice(stock=s,firstadviceyear=2001,lastadviceyear=lay+1, include.replaced = FALSE)

_Figure 1c western horse mackerel. Top: comparison of (max) scientific advice, TAC (or sum of unilateral quota) and Total Catch. Bottom: percentage deviation from ICES advice, CoA is Catch over Advice, ToA is TAC over Advice. _

@@

@@

_Figure 4a Atlanto-scandian herring. Summary of most recent assessment_

@@

# s   <- "her-noss"

plot_history(stock=s,
             firstassessyear=fay,
             lastassessyear=lay, 
             firstyear=fy, 
             lastyear=ly, 
             include.benchmark = TRUE, 
             include.replaced = FALSE, 
             plot = c("stocksize", "fishingpressure"), 
             plot.uncertainty=TRUE)

@@

_Figure 4b Atlanto-scandian herring. History of assessments. Red is most recent assessment, black is earlier assessments and blue is benchmarks. _

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# s   <- "her-noss"

plot_advice(stock=s,firstadviceyear=2001,lastadviceyear=lay+1, include.replaced = FALSE)

_Figure 4c Atlanto-scandian herring. Top: comparison of (max) scientific advice, TAC (or sum of unilateral quota) and Total Catch. Bottom: percentage deviation from ICES advice, CoA is Catch over Advice, ToA is TAC over Advice. _

@@

_Table 4 Atlanto-scandian herring. History of advice, tac and catch._

### 2022-12-17 Rmd/ICES advice and assessment summaries WGWIDE 2019.Rmd
Restructured into Rmd folder

>>>>

    # generate variables
    mutate(
      variable = ifelse(refpoint %in% c("blim","bpa","msybtrigger"), "stocksize", NA),
      variable = ifelse(refpoint %in% c("flim", "fpa", "fmsy"), "fishingpressure", variable) ) %>% 
    filter(variable %in% plot) %>% 
    mutate(variable = factor(variable, levels=plot, ordered=TRUE)) %>%
